### 2014-09-15 PrivacyProtection-2014-09-09.tex

\subsubsection{Humans}

>>>>

\subsubsection{Actors}
\label{subsubsection:humans}

This section outlines the human actors previously introduced within the IT system architecture (\ref{subsubsection:it-systems}).
It is described which individual interests they have invested in monitoring systems comparable to the Live+Gov system. 
Also the additional actor \textit{Criminal} is introduced as an possible obstacle.

\textbf{Citizen:}
\begin{itemize}
\item legal right to privacy
\item no spam
\item no stalking
\item no loss / gain of money
\item physical wellbeing / personal health (attack because someone knows your gps location)
\item transparency: who has my data
\item good pricing of insurance policies
\end{itemize}

In short, Citizens are interested in ...
\begin{itemize}
\item ... confidential use of privacy sensitive data
\item ... legitimate use of privacy sensitive data
\item ... proportional use of privacy sensitive data
\item ... successful use of privacy sensitive data
\end{itemize}

\textbf{Criminal:}
Criminals are persons who do not have legal access to the IT systems of a proposed monitoring system.
Usually, monetary interests lead their activities.
For example they want to obtain access to critical systems to steal sensitive data or to get the system under their control.
Controlled systems could be leased as part of a bot net. 
Stolen data could simply be sold as is or used for illegitimate purposes, e.g. spam or phishing attacks - or excessive data mining.

Because Local Authorities are involved in the general outline of a public monitoring system, the possibility for politically motivated attacks cannot be ignored. 
Criminals could want to harm or destroy the systems in order to damage the reputation of Local Authorities (politicians or other officials) or to make a political statement of their own, e.g. "Stop Surveillance!".

Another possible motivation for criminal activities could be social appreciation.
A hacker could attack critical infrastructure just to show his skills.

In short, Criminals are interested in ...
\begin{itemize}
\item ... financial profit
\item ... high social standing
\item ... political power
\end{itemize}

\textbf{System Provider:}
System Providers provide and operate the technical infrastructure (hardware and software) of the proposed monitoring system.
They are normal companies which offer to provide a service, so different roles of employees are involved:
an administrator, who maintains and operates the running system;
a programmer/developer, who develops the system;
a support manager, who handles customer relations;
...

As companies, they follow typical business objectives. 
They are interested in gaining financial profit, which heavily depends on the customer's satisfaction.
But it also depends on the happiness of their employees. 
Employees have a claim to professional excellence.
They want to deliver a good job within their means.
This effects product quality and thus effects customer satisfaction.
If employees cannot satisfy their demand for professional excellence, they might get discontent, deliver poor work or produce higher costs through sick days.
The worst case scenario could be, that a discontent employee gets angry and steals data or harms the running systems.

In short, System Providers are interested in ...
\begin{itemize}
\item ... financial profit
\item ... good working conditions
\item ... professional excellence
\end{itemize}

\textbf{Local Authority:}

In short, Local Authorities are interested in ...
\begin{itemize}
\item ... business intelligence (profit, RoI)
\item ... political reputation
\end{itemize}
